### 2019-09-28 conflog.tex
adds section about facility contingency
Dinner Descriptions

@@

\textbf{Thursday Night}\\
\textbf{Friday Night}\\
\textbf{Saturday Night}\\

\subsection{Travel and Transportation}

>>>>

\textbf{The I Hotel and Conference Center}\\
The IHotel offers a unique, flexible, meeting space and a variety of small touches that make any meeting, social gathering or event in Champaign-Urbana a flawless and memorable experience.\\

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{ihotel.jpg}
    \caption{I Hotel}
    \label{fig:beckman}
\end{figure}

@@

\textbf{Thursday Night}\\
Communicating the science of nuclear energy remains one of the chief challenges of our field, which is why the opening dinner of this conference will focus on science communication and the people behind the science. Science communication requires more than the recitation of raw data to be effective. By telling our own, diverse backstories, we become more effective science communicators. Speakers will be chosen which emphasize this fact and will be asked to speak to their own backstory as a nuclear advocate and how this story makes them a more effective communicator.
\textbf{Friday Night}\\
The second dinner will be themed around networking and professional-development, and how these critical tools have value beyond finding jobs. Communities like ANS thrive on the exchange of ideas and knowledge, and the student conference serves the vital role of connecting the burgeoning minds of the next generation with the wisdom of established professionals. This dinner will consist of tables organized by company/national lab to allow students and professionals to mingle, promoting the exchange of ideas. 
\textbf{Saturday Night}\\
The closing dinner of the conference will be a call to action for student attendees. Ours is a generation faced with challenges on a scale never witnessed by humanity, and we will only successfully address these challenges through the engagement of as many bright young minds as possible. The speakers for this night will be asked to address ways we all can take individual responsibility for the grand challenges of our age, using our own unique skills to tackle problems like climate change and energy poverty from every angle imaginable. 
\subsection{Travel and Transportation}
